\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-06-16 draft.tex
revise conclusion

\section{Conclusion}
\label{sec:concl}
I have shown that the legislature both breaks trade agreements with a higher probability and sets higher trade war tariffs when lobbying activity increases, while the probability with which it breaks agreements (or fails to ratify them) decreases in the domestic trade agreement tariff. Because the lobby decreases its effort in response to higher trade agreement tariffs, the executives face a trade-off between the welfare derived while a trade agreement is in force and the probability with which the agreement actually enters into force.

I have also shown that in a policy-making structure in which power is shared, a less politically-motivated executive can utilize an international trade agreement to reduce the political pressure on the ratifying body and therefore increase the probability that the agreement will remain in force. Thus, in a model with a richer description of government structure, a political-commitment role for trade agreements can arise.

>>>>

\section{Conclusion}
\label{sec:concl}
I have shown that the legislature both breaks trade agreements with a higher probability and sets higher trade war tariffs when lobbying activity increases, while the probability with which it breaks agreements decreases in the domestic trade agreement tariff. Because the lobby decreases its effort in response to higher trade agreement tariffs, the executives face a trade-off between the welfare derived while a trade agreement is in force and the probability with which the agreement actually enters into force.

I have also shown that in a policy-making structure in which power is shared, a less politically-motivated executive can utilize an international trade agreement to reduce the political pressure on the ratifying body and therefore increase the probability that the agreement will remain in force. Thus, in a model with a richer description of government structure, a broad political-commitment role for trade agreements can arise.
